### 2023-02-11 DraftDataAnalysis.Rmd
Add files via upload

---
title: "DraftDataAnalysis"
author: "Kyle McCullough"
date: "2023-02-11"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### 2023-03-03 DraftDataAnalysis.Rmd
Add files via upload

@@
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+#Loading cleaned draft data
+```{r}
+library(tidyverse)
+library(readxl)
+
+draft = read_excel('1993-2022draftStats.xlsx', col_names = TRUE)
+draft
+
+draft$wAV[is.na(draft$wAV)] = 0
+draft$DrAV[is.na(draft$DrAV)] = 0
+draft$G[is.na(draft$G)] = 0
+draft$Cmp[is.na(draft$Cmp)] = 0
+draft$PassAtt[is.na(draft$PassAtt)] = 0
+draft$PassYds[is.na(draft$PassYds)] = 0
+draft$PassTD[is.na(draft$PassTD)] = 0
+draft$`Int(O)`[is.na(draft$`Int(O)`)] = 0
+draft$RushAtt[is.na(draft$RushAtt)] = 0
+draft$RushYds[is.na(draft$RushYds)] = 0
+draft$RushTD[is.na(draft$RushTD)] = 0
+draft$Rec[is.na(draft$Rec)] = 0
+draft$RecYds[is.na(draft$RecYds)] = 0
+draft$RecTD[is.na(draft$RecTD)] = 0
+draft$Solo[is.na(draft$Solo)] = 0
+draft$`Int(D)`[is.na(draft$`Int(D)`)] = 0
+draft$Sk[is.na(draft$Sk)] = 0
+draft$`College/Univ`[3051] = "Bethel (TN)"
+draft$`College/Univ`[3145] = "Lousiana-Lafayette"
+draft$`College/Univ`[3149] = "Regina"
+draft$`College/Univ`[3170] = "Lousiana-Lafayette"
+draft$`College/Univ`[3229] = "California Polytechnic State"
+draft$`College/Univ`[3231] = "Missouri Western State"
+draft$`College/Univ`[3249] = "Georgia State"
+draft$`College/Univ`[3261] = "Alabama-Birmingham"
+draft$`College/Univ`[3516] = "Colorado State-Pueblo"
+draft$`College/Univ`[3555] = "Northeastern State"
+draft$`College/Univ`[4259] = "No college"
+draft$`College/Univ`[4818] = "No college"
+draft$`College/Univ`[6046] = "Eastern Michigan"
+draft$`College/Univ`[6843] = "Trinity International"
+draft$`College/Univ`[7097] = "Trinity International"
+draft$`College/Univ`[7296] = "Clark Atlanta"
+
+this = draft %>%
+  mutate(Fran = Tm)
+
+this = this %>%
+  mutate(Fran = replace(Fran, Fran == "PHO", "ARI")) %>%
+  mutate(Fran = replace(Fran, Fran == "SDG", "LAC")) %>%
+  mutate(Fran = replace(Fran, Fran == "STL", "LAR")) %>%
+  mutate(Fran = replace(Fran, Fran == "RAM", "LAR")) %>%
+  mutate(Fran = replace(Fran, Fran == "OAK", "LVR")) %>%
+  mutate(Fran = replace(Fran, Fran == "RAI", "LVR"))
 ```
+
+Pro Football Reference has provided a wAV stat which is the weigthed average value
+of each player and this is what I will be using to show how productive of a career
+a player had.
+```{r}
+draftPick = draft %>%
+  filter(Draft < 2011)
+
+ggplot(draftPick, aes(Pick, wAV)) +
+  geom_point()
+reg = lm(draft$wAV~draft$Pick)
+jtools :: summ(reg)
+anova(reg)
+```
+
+Which teams have had the most successful draft picks?
+```{r}
+teamDraftSuccess = this %>%
+  group_by(Fran) %>%
+  summarise(averagewAV = mean(wAV))
+teamDraftSuccess = arrange(teamDraftSuccess, desc(averagewAV))
+teamDraftSuccess
+```

### 2023-03-03 NFLdraftDataCleaning.R
Add files via upload

@@ -1,0 +1,175 @@
+#NFL draft data cleaning
+library(tidyverse)
+library(readxl)
+
+draft = read_excel('1993-2022draftStats.xlsx', col_names = TRUE)
+draft
+
+#Cleaning of data
+#-Fixing NA values
+colnames(draft)
+which(is.na(draft$Draft))#none
+which(is.na(draft$Rnd))#none
+which(is.na(draft$Pick))#none
+which(is.na(draft$Tm))#none
+which(is.na(draft$Player))#none
+which(is.na(draft$Pos))#none
+which(is.na(draft$Age))#not as important so we can leave as NA
+draft %>%
+  filter(is.na(draft$Age))
+
+which(is.na(draft$To))#not as important so we can leave as NA
+draft %>%
+  filter(is.na(draft$To))
+
+which(is.na(draft$AP1))#none
+which(is.na(draft$PB))#none
+which(is.na(draft$St))#none
+which(is.na(draft$wAV))#important need to change
+draft %>%
+  filter(is.na(draft$wAV))
+#After looking at the data it seems like a majority of the reason wAV is NA is
+#because the player did not play any games or they got cut etc. So I am going
+#to set every NA value to 0
+draft$wAV[is.na(draft$wAV)] = 0
+which(is.na(draft$wAV))#data is fixed to none
+
+which(is.na(draft$DrAV))#important need to change
+draft %>%
+  filter(is.na(draft$DrAV))
+#After looking at the data it seems that like a majority of the reason DrAV is NA
+#is because the player did not play any games or they got cut or they were traded
+#before playing for the drafted team. So I am going to change all values to 0
+draft$DrAV[is.na(draft$DrAV)] = 0
+which(is.na(draft$DrAV))#data is fixed to none
+
+which(is.na(draft$G))#needs change
+draft %>%
+  filter(is.na(draft$G))
+#A majority of the people that have NA for games never played in any, so I
+#am changing all NA's to 0
+draft$G[is.na(draft$G)] = 0
+which(is.na(draft$G))#data is fixed to none
+
+which(is.na(draft$Cmp))#same thing as above
+draft$Cmp[is.na(draft$Cmp)] = 0
+which(is.na(draft$Cmp))
+
[…]

### 2023-03-03 NFLdraftDataAnalysis.R
Delete NFLdraftDataAnalysis.R

@@ -1,131 +1,0 @@
-#NFL draft data cleaning
-library(tidyverse)
-library(readxl)
-
-draft = read_excel('1993-2022draftStats.xlsx', col_names = TRUE)
-draft
-
-#Cleaning of data
-#-Fixing NA values
-colnames(draft)
-which(is.na(draft$Draft))#none
-which(is.na(draft$Rnd))#none
-which(is.na(draft$Pick))#none
-which(is.na(draft$Tm))#none
-which(is.na(draft$Player))#none
-which(is.na(draft$Pos))#none
-which(is.na(draft$Age))#not as important so we can leave as NA
-draft %>%
-  filter(is.na(draft$Age))
-
-which(is.na(draft$To))#not as important so we can leave as NA
-draft %>%
-  filter(is.na(draft$To))
-
-which(is.na(draft$AP1))#none
-which(is.na(draft$PB))#none
-which(is.na(draft$St))#none
-which(is.na(draft$wAV))#important need to change
-draft %>%
-  filter(is.na(draft$wAV))
-#After looking at the data it seems like a majority of the reason wAV is NA is
-#because the player did not play any games or they got cut etc. So I am going
-#to set every NA value to 0
-draft$wAV[is.na(draft$wAV)] = 0
-which(is.na(draft$wAV))#data is fixed to none
-
-which(is.na(draft$DrAV))#important need to change
-draft %>%
-  filter(is.na(draft$DrAV))
-#After looking at the data it seems that like a majority of the reason DrAV is NA
-#is because the player did not play any games or they got cut or they were traded
-#before playing for the drafted team. So I am going to change all values to 0
-draft$DrAV[is.na(draft$DrAV)] = 0
-which(is.na(draft$DrAV))#data is fixed to none
-
-which(is.na(draft$G))#needs change
-draft %>%
-  filter(is.na(draft$G))
-#A majority of the people that have NA for games never played in any, so I
-#am changing all NA's to 0
-draft$G[is.na(draft$G)] = 0
-which(is.na(draft$G))#data is fixed to none
-
-which(is.na(draft$Cmp))#same thing as above
-draft$Cmp[is.na(draft$Cmp)] = 0
-which(is.na(draft$Cmp))
-
[…]

### 2023-03-27 NFLdraftDataCleaning.R
Delete NFLdraftDataCleaning.R

@@ -1,175 +1,0 @@
-#NFL draft data cleaning
-library(tidyverse)
-library(readxl)
-
-draft = read_excel('1993-2022draftStats.xlsx', col_names = TRUE)
-draft
-
-#Cleaning of data
-#-Fixing NA values
-colnames(draft)
-which(is.na(draft$Draft))#none
-which(is.na(draft$Rnd))#none
-which(is.na(draft$Pick))#none
-which(is.na(draft$Tm))#none
-which(is.na(draft$Player))#none
-which(is.na(draft$Pos))#none
-which(is.na(draft$Age))#not as important so we can leave as NA
-draft %>%
-  filter(is.na(draft$Age))
-
-which(is.na(draft$To))#not as important so we can leave as NA
-draft %>%
-  filter(is.na(draft$To))
-
-which(is.na(draft$AP1))#none
-which(is.na(draft$PB))#none
-which(is.na(draft$St))#none
-which(is.na(draft$wAV))#important need to change
-draft %>%
-  filter(is.na(draft$wAV))
-#After looking at the data it seems like a majority of the reason wAV is NA is
-#because the player did not play any games or they got cut etc. So I am going
-#to set every NA value to 0
-draft$wAV[is.na(draft$wAV)] = 0
-which(is.na(draft$wAV))#data is fixed to none
-
-which(is.na(draft$DrAV))#important need to change
-draft %>%
-  filter(is.na(draft$DrAV))
-#After looking at the data it seems that like a majority of the reason DrAV is NA
-#is because the player did not play any games or they got cut or they were traded
-#before playing for the drafted team. So I am going to change all values to 0
-draft$DrAV[is.na(draft$DrAV)] = 0
-which(is.na(draft$DrAV))#data is fixed to none
-
-which(is.na(draft$G))#needs change
-draft %>%
-  filter(is.na(draft$G))
-#A majority of the people that have NA for games never played in any, so I
-#am changing all NA's to 0
-draft$G[is.na(draft$G)] = 0
-which(is.na(draft$G))#data is fixed to none
-
-which(is.na(draft$Cmp))#same thing as above
-draft$Cmp[is.na(draft$Cmp)] = 0
-which(is.na(draft$Cmp))
-
[…]

### 2023-03-27 DraftDataAnalysis.Rmd
Add files via upload

@@
 library(readxl)
+library(ggplot2)
+library(nflplotR)
 
@@
   mutate(Fran = replace(Fran, Fran == "RAI", "LVR"))
+
+draft = draft %>%
+  mutate(Pos = replace(Pos, Pos == "S", "DB")) %>%
+  mutate(Pos = replace(Pos, Pos == "CB", "DB"))
 ```
@@
 
-ggplot(draftPick, aes(Pick, wAV)) +
-  geom_point()
-reg = lm(draft$wAV~draft$Pick)
-jtools :: summ(reg)
-anova(reg)
+reg1 = lm(draftPick$wAV~draftPick$Pick)
+reg2 = lm(draftPick$wAV~log(draftPick$Pick))
+jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))
+
+draftPick %>% ggplot(aes(x = Pick, y = wAV)) +
+  geom_point() + 
+  stat_smooth(method = lm,
+              formula = y~log(x),
+              se = TRUE,
+              ) +
+  labs(title = "Average value of each draft pick",
+       subtitle = "Data from 1993 to 2010")
+
+plot.fitted <- function(lmod) {
+  require(ggplot2,dplyr)
+  df = lmod$model
+  title = paste("Residuals vs. Fits (Dependent Variable: ",
+                names(df)[1],
+                ")",
+                sep = "")
+  pr <- df %>% ggplot(aes(x = fitted(lmod), y = resid(lmod))) +
+    geom_ribbon(aes(ymin = -sigma(lmod), ymax = sigma(lmod)),
+                fill = "gray",
+                alpha = .5) +
+    geom_ribbon(aes(ymin = -sigma(lmod) * 2, ymax = sigma(lmod) * 2),
+                fill = "lightgray",
+                alpha = .5) +
+    geom_point() +
+    theme_classic() +
+    ggtitle(title) +
+    ylab("Residules") +
+    xlab("Fitted") +
+    geom_hline(yintercept = 0,
+               linetype = "solid",
+               color = "black")
+  return(pr)  
+}
+
+plot.fitted(reg1)
+plot.fitted(reg2)
+
+b = reg2$fitted.values
+PickValue = tibble(wAV = b, Pick = 1:4489)
+PickValue = PickValue %>%
+  filter(Pick < 256)
+PickValue
+```
+```{r}
+draftPick %>%
+  filter(Draft > 1993) %>%
+  group_by(Rnd) %>%
+  summarise(averagewAV = mean(wAV))
 ```
@@
 teamDraftSuccess
+
+teamDraftSuccess %>%
+  ggplot2::ggplot(aes(reorder(Fran, averagewAV), averagewAV)) +
+  nflplotR::geom_nfl_logos(aes(team_abbr = Fran), width = 0.065, alpha = 0.7) +
+  ggplot2::labs(title = "Average Value of Player Drafted by each Franchise",
+       subtitle = "From 1993 to 2022",
+       y = "Average Value per Player drafted",
+       x = "Franchise") +
+  ggplot2::theme(plot.title = ggplot2::element_text(face = "bold"),
+                 axis.text.x = element_blank(),
+                 axis.ticks.x = element_blank())
 ```
+
+Which college has the best nfl prospects?
+```{r}
+draft %>%
+  group_by(`College/Univ`) %>%
+  summarise(sumwAV = sum(wAV)) %>%
+  arrange(desc(sumwAV))
+
+draft %>%
+  filter(Draft < 2011) %>%
+  group_by(`College/Univ`) %>%
+  filter(n() > 19) %>%
+  summarise(averagewAV = mean(wAV)) %>%
+  arrange(desc(averagewAV))
+```
+
+```{r}
+draft %>%
+  filter(Pos == "WR") %>%
+  group_by(`College/Univ`) %>%
+  summarise(sumwAV = sum(wAV)) %>%
+  arrange(desc(sumwAV))
+
+draft %>%
+  filter(Pos == "WR") %>%
+  filter(`College/Univ` == "Ohio St.") %>%
+  arrange(desc(wAV))
+
+draft %>%
+  filter(Pos == "WR") %>%
+  filter(`College/Univ` == "LSU") %>%
+  arrange(desc(wAV))
+```
+```{r}
+draft %>%
+  filter(Pos == "DB") %>%
+  group_by(`College/Univ`) %>%
+  summarise(sumwAV = sum(wAV)) %>%
+  arrange(desc(sumwAV))
+
+draft %>%
+  filter(Pos == "DB") %>%
+  filter(`College/Univ` == "Alabama") %>%
+  arrange(desc(wAV))
+
+draft %>%
+  filter(Pos == "DB") %>%
+  filter(`College/Univ` == "LSU") %>%
+  arrange(desc(wAV))
+```
+
+```{r}
+draft %>%
+  filter(`College/Univ` == "Boston Col.") %>%
+  filter(Draft < 2011) %>%
+  arrange(desc(wAV))
+
+draft %>%
+  filter(`College/Univ` == "Miami (FL)") %>%
+  filter(Draft < 2011) %>%
+  arrange(desc(wAV))
+```
+
+```{r}
+draft %>%
+  filter(Player == "Tre'Davious White")
+```

### 2023-03-27 NFLdraftDataCleaning.R

@@ -1,0 +1,178 @@
+#NFL draft data cleaning
+library(tidyverse)
+library(readxl)
+
+draft = read_excel('1993-2022draftStats.xlsx', col_names = TRUE)
+draft
+
+#Cleaning of data
+#-Fixing NA values
+colnames(draft)
+which(is.na(draft$Draft))#none
+which(is.na(draft$Rnd))#none
+which(is.na(draft$Pick))#none
+which(is.na(draft$Tm))#none
+which(is.na(draft$Player))#none
+which(is.na(draft$Pos))#none
+which(is.na(draft$Age))#not as important so we can leave as NA
+draft %>%
+  filter(is.na(draft$Age))
+
+which(is.na(draft$To))#not as important so we can leave as NA
+draft %>%
+  filter(is.na(draft$To))
+
+which(is.na(draft$AP1))#none
+which(is.na(draft$PB))#none
+which(is.na(draft$St))#none
+which(is.na(draft$wAV))#important need to change
+draft %>%
+  filter(is.na(draft$wAV))
+#After looking at the data it seems like a majority of the reason wAV is NA is
+#because the player did not play any games or they got cut etc. So I am going
+#to set every NA value to 0
+draft$wAV[is.na(draft$wAV)] = 0
+which(is.na(draft$wAV))#data is fixed to none
+
+which(is.na(draft$DrAV))#important need to change
+draft %>%
+  filter(is.na(draft$DrAV))
+#After looking at the data it seems that like a majority of the reason DrAV is NA
+#is because the player did not play any games or they got cut or they were traded
+#before playing for the drafted team. So I am going to change all values to 0
+draft$DrAV[is.na(draft$DrAV)] = 0
+which(is.na(draft$DrAV))#data is fixed to none
+
+which(is.na(draft$G))#needs change
+draft %>%
+  filter(is.na(draft$G))
+#A majority of the people that have NA for games never played in any, so I
+#am changing all NA's to 0
+draft$G[is.na(draft$G)] = 0
+which(is.na(draft$G))#data is fixed to none
+
+which(is.na(draft$Cmp))#same thing as above
+draft$Cmp[is.na(draft$Cmp)] = 0
+which(is.na(draft$Cmp))
+
[…]

### 2023-04-14 DraftDataAnalysis.Rmd
Add files via upload

@@
 
-draft = draft %>%
-  mutate(Pos = replace(Pos, Pos == "S", "DB")) %>%
-  mutate(Pos = replace(Pos, Pos == "CB", "DB"))
+#draft = draft %>%
+  #mutate(Pos = replace(Pos, Pos == "S", "DB")) %>%
+  #mutate(Pos = replace(Pos, Pos == "CB", "DB")) %>%
+  #mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
+  #mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
+  #mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
+  #mutate(Pos = replace(Pos, Pos == "OLB", "LB")) %>%
+  #mutate(Pos = replace(Pos, Pos == "ILB", "LB"))
+```
+```{r}
+draft %>%
+  filter(Pos == c("K")) %>%
+  #filter(wAV <= 9) %>%
+  filter(wAV >= 35) %>%
+  summarise(averageAP1 = mean(AP1), averagePB = mean(PB), averageSt = mean(St), averageG = mean(G), averageCompPer = mean(Cmp/PassAtt), averagePassYds = mean(PassYds), averagePassTds = mean(PassTD), averageIntO = mean(`Int(O)`), averageRushYds = mean(RushYds), averageRushTds = mean(RushTD), averageRec = mean(Rec), averageRecYds = mean(RecYds), averageRecTds = mean(RecTD), averageSolo = mean(Solo), averageIntD = mean(`Int(D)`), averageSk = mean(Sk))
 ```
@@
 b = reg2$fitted.values
-PickValue = tibble(wAV = b, Pick = 1:4489)
+PickValue = tibble(Pick = 1:4489, wAV = b)
 PickValue = PickValue %>%
@@
 ```
+
 ```{r}
@@
   group_by(Rnd) %>%
+  summarise(averagewAV = mean(wAV))
+```
+```{r}
+draftPick %>%
+  group_by(Pick) %>%
   summarise(averagewAV = mean(wAV))
@@
 draft %>%
-  filter(Player == "Tre'Davious White")
+  filter(Pos == c("K"))%>%
+  arrange(desc(wAV))
+draft %>%
+  filter(Player == "Cameron Heyward")
 ```
+
+Which Positions have the most value?
+```{r}
+draft %>%
+  group_by(Pos) %>%
+  summarise(averagewAV = mean(wAV)) %>%
+  arrange(desc(averagewAV))
+```
+Which was the best NFL draft?
+```{r}
+draft %>%
+  group_by(Draft) %>%
+  summarize(sumwAV = sum(wAV)) %>%
+  arrange(desc(sumwAV))
+draft %>%
+  filter(Draft == 2009) %>%
+  arrange(desc(wAV))
+draft %>%
+  filter(Pos == "WR") %>%
+  filter(wAV == 4)
+```
+When do positions tend to get drafted?
+```{r}
+draft %>%
+  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
+  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
+  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
+  group_by(Pos) %>%
+  summarise(avgDraftPos = mean(Pick)) %>%
+  arrange(avgDraftPos)
+```
+When the first player at each position gets picked on average?
+```{r}
+draft %>%
+  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
+  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
+  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
+  arrange(Pick) %>%
+  group_by(Pos, Draft) %>%
+  mutate(NumPosInDraft = n()) %>%
+  mutate(PosDraft = 1:NumPosInDraft) %>%
+  arrange(PosDraft) %>%
+  ungroup(Draft) %>%
+  filter(PosDraft == 1) %>%
+  summarise(avgPick = mean(Pick)) %>%
+  arrange(avgPick)
+```
+
+When should positions really be drafted?
+```{r}
+draft %>%
+  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
+  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
+  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
+  filter(Draft < 2011) %>%
+  filter(Rnd == 1) %>%
+  group_by(Pos) %>%
+  summarize(avgwAV = mean(wAV)) %>%
+  arrange(desc(avgwAV))
+```
+
+Position: T
+```{r}
+draftT = draft %>%
+  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
+  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
+  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
+  filter(Pos == "T") %>%
+  filter(Draft < 2011) %>% 
+  arrange(Pick)
+
+attach(draftT) 
+reg1 = lm(draftT$wAV~draftT$Pick)
+reg2 = lm(draftT$wAV~log(draftT$Pick))
+jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))
+
+draftT %>% ggplot(aes(x = Pick, y = wAV)) +
+  geom_point() + 
+  stat_smooth(method = lm,
+              formula = y~log(x),
+              se = TRUE,
+              )
+
+reg = lm(draftT$wAV~log(draftT$Pick))
+
+b = predict(reg)
+PickValue = tibble(Pick = 1:350, wAV = b)
+PickValue = PickValue %>%
+  filter(Pick < 256)
+PickValue
+```
+```{r}
+draftT = draft %>%
+  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
+  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
+  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
+  filter(Pos == "T") %>%
+  filter(Draft < 2011)
+
+attach(draftT) 
+reg1 = lm(draftT$wAV~draftT$Pick)
+reg2 = lm(draftT$wAV~log(draftT$Pick))
+jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))
+
+draftT %>% ggplot(aes(x = Pick, y = wAV)) +
+  geom_point() + 
+  stat_smooth(method = lm,
+              formula = y~log(x),
+              se = TRUE,
+              )
+
+draftQB = draft %>%
+  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
+  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
+  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
+  filter(Pos == "QB") %>%
+  filter(Draft < 2011)
+
+draftDE = draft %>%
+  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
+  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
+  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
+  filter(Pos == "DE") %>%
+  filter(Draft < 2011)
+```
+```{r}
+draftPos = draft %>%
+  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
+  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
+  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
+  filter(Pos == c("T", "QB", "DE")) %>%
+  filter(Draft < 2011)
+
+draftPos %>% ggplot(aes(x = Pick, y = wAV)) +
+  geom_jitter(aes(draftT$Pick, draftT$wAV), colour = "red") + 
+  stat_smooth(aes(draftT$Pick, draftT$wAV, col = "red"),
+              method = lm,
+              formula = y~log(x),
+              se = TRUE,
+              ) +
+  geom_jitter(aes(draftQB$Pick, draftQB$wAV), colour = "blue") + 
+  stat_smooth(aes(draftQB$Pick, draftQB$wAV, col = "blue"),
+              method = lm,
+              formula = y~log(x),
+              se = TRUE,
+              )
+```
+```{r}
+draft %>%
+  filter(Player == "Joe Webb")
+```

### 2023-05-07 NFLdraftDataCleaning.R
Delete NFLdraftDataCleaning.R

@@ -1,178 +1,0 @@
-#NFL draft data cleaning
-library(tidyverse)
-library(readxl)
-
-draft = read_excel('1993-2022draftStats.xlsx', col_names = TRUE)
-draft
-
-#Cleaning of data
-#-Fixing NA values
-colnames(draft)
-which(is.na(draft$Draft))#none
-which(is.na(draft$Rnd))#none
-which(is.na(draft$Pick))#none
-which(is.na(draft$Tm))#none
-which(is.na(draft$Player))#none
-which(is.na(draft$Pos))#none
-which(is.na(draft$Age))#not as important so we can leave as NA
-draft %>%
-  filter(is.na(draft$Age))
-
-which(is.na(draft$To))#not as important so we can leave as NA
-draft %>%
-  filter(is.na(draft$To))
-
-which(is.na(draft$AP1))#none
-which(is.na(draft$PB))#none
-which(is.na(draft$St))#none
-which(is.na(draft$wAV))#important need to change
-draft %>%
-  filter(is.na(draft$wAV))
-#After looking at the data it seems like a majority of the reason wAV is NA is
-#because the player did not play any games or they got cut etc. So I am going
-#to set every NA value to 0
-draft$wAV[is.na(draft$wAV)] = 0
-which(is.na(draft$wAV))#data is fixed to none
-
-which(is.na(draft$DrAV))#important need to change
-draft %>%
-  filter(is.na(draft$DrAV))
-#After looking at the data it seems that like a majority of the reason DrAV is NA
-#is because the player did not play any games or they got cut or they were traded
-#before playing for the drafted team. So I am going to change all values to 0
-draft$DrAV[is.na(draft$DrAV)] = 0
-which(is.na(draft$DrAV))#data is fixed to none
-
-which(is.na(draft$G))#needs change
-draft %>%
-  filter(is.na(draft$G))
-#A majority of the people that have NA for games never played in any, so I
-#am changing all NA's to 0
-draft$G[is.na(draft$G)] = 0
-which(is.na(draft$G))#data is fixed to none
-
-which(is.na(draft$Cmp))#same thing as above
-draft$Cmp[is.na(draft$Cmp)] = 0
-which(is.na(draft$Cmp))
-
[…]

### 2023-05-07 DraftDataAnalysis.Rmd
Add files via upload

@@
 ```{r}
-draftPick %>%
+roundPick = draftPick %>%
   filter(Draft > 1993) %>%
@@
   summarise(averagewAV = mean(wAV))
+roundPick
 ```
@@
 When should positions really be drafted?
+AveragewAV for first round talent per Position
 ```{r}
@@
 Position: T
+wAV as the Draft goes on and then the wAV per each player per position in draft
 ```{r}
@@
 
-draftT %>% ggplot(aes(x = Pick, y = wAV)) +
+#wAV per Pick per tackle
+p = draftT %>% ggplot(aes(x = Pick, y = wAV)) +
   geom_point() + 
@@
               )
+p
+p2 = ggplot_build(p)
+p2$data[[2]]
 
-reg = lm(draftT$wAV~log(draftT$Pick))
+draftTOrder = draftT %>%
+  group_by(Draft) %>%
+  mutate(NumPosInDraft = n()) %>%
+  mutate(PosDraft = 1:NumPosInDraft) %>%
+  arrange(PosDraft) %>%
+  ungroup(Draft)
 
-b = predict(reg)
-PickValue = tibble(Pick = 1:350, wAV = b)
-PickValue = PickValue %>%
-  filter(Pick < 256)
-PickValue
-```
-```{r}
-draftT = draft %>%
-  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
-  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
-  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
-  filter(Pos == "T") %>%
-  filter(Draft < 2011)
-
-attach(draftT) 
-reg1 = lm(draftT$wAV~draftT$Pick)
-reg2 = lm(draftT$wAV~log(draftT$Pick))
+attach(draftTOrder) 
+reg1 = lm(draftTOrder$wAV~draftTOrder$PosDraft)
+reg2 = lm(draftTOrder$wAV~log(draftTOrder$PosDraft))
 jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))
 
-draftT %>% ggplot(aes(x = Pick, y = wAV)) +
+p3 = draftTOrder %>%
+  ggplot(aes(x=PosDraft, y=wAV)) +
   geom_point() +
@@
               )
-
+p3
+p4 = ggplot_build(p3)
+p4$data[[2]]
+```
+Position: QB
+```{r}
 draftQB = draft %>%
@@
   filter(Pos == "QB") %>%
-  filter(Draft < 2011)
+  filter(Draft < 2011) %>%
+  arrange(Pick)
 
+attach(draftQB) 
+reg1 = lm(draftQB$wAV~draftQB$Pick)
+reg2 = lm(draftQB$wAV~log(draftQB$Pick))
+jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))
+
+p = draftQB %>% ggplot(aes(x = Pick, y = wAV)) +
+  geom_point() + 
+  stat_smooth(method = lm,
+              formula = y~log(x),
+              se = TRUE,
+              )
+p
+p2 = ggplot_build(p)
+p2$data[[2]]
+
+draftQBOrder = draftQB %>%
+  group_by(Draft) %>%
+  mutate(NumPosInDraft = n()) %>%
+  mutate(PosDraft = 1:NumPosInDraft) %>%
+  arrange(PosDraft) %>%
+  ungroup(Draft)
+
+attach(draftQBOrder) 
+reg1 = lm(draftQBOrder$wAV~draftQBOrder$PosDraft)
+reg2 = lm(draftQBOrder$wAV~log(draftQBOrder$PosDraft))
+jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))
+
+p3 = draftQBOrder %>%
+  ggplot(aes(x=PosDraft, y=wAV)) +
+  geom_point() +
+  stat_smooth(method = lm,
+              formula = y~log(x),
+              se = TRUE,
+              )
+p3
+p4 = ggplot_build(p3)
+p4$data[[2]]
+```
+Position: DE
+```{r}
 draftDE = draft %>%
@@
   filter(Pos == "DE") %>%
-  filter(Draft < 2011)
+  filter(Draft < 2011) %>%
+  arrange(Pick)
+
+attach(draftDE) 
+reg1 = lm(draftDE$wAV~draftDE$Pick)
+reg2 = lm(draftDE$wAV~log(draftDE$Pick))
+jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))
+
+p = draftDE %>% ggplot(aes(x = Pick, y = wAV)) +
+  geom_point() + 
+  stat_smooth(method = lm,
+              formula = y~log(x),
+              se = TRUE,
+              )
+p
+p2 = ggplot_build(p)
+p2$data[[2]]
+
+draftDEOrder = draftDE %>%
+  group_by(Draft) %>%
+  mutate(NumPosInDraft = n()) %>%
+  mutate(PosDraft = 1:NumPosInDraft) %>%
+  arrange(PosDraft) %>%
+  ungroup(Draft)
+
+attach(draftDEOrder) 
+reg1 = lm(draftDEOrder$wAV~draftDEOrder$PosDraft)
+reg2 = lm(draftDEOrder$wAV~log(draftDEOrder$PosDraft))
+jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))
+
+p3 = draftDEOrder %>%
+  ggplot(aes(x=PosDraft, y=wAV)) +
+  geom_point() +
+  stat_smooth(method = lm,
+              formula = y~log(x),
+              se = TRUE,
+              )
+p3
+p4 = ggplot_build(p3)
+p4$data[[2]]
 ```
+Position: DT
 ```{r}
-draftPos = draft %>%
+draftDT = draft %>%
   mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
@@
   mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
-  filter(Pos == c("T", "QB", "DE")) %>%
-  filter(Draft < 2011)
+  filter(Pos == "DT") %>%
+  filter(Draft < 2011) %>%
+  arrange(Pick)
 
-draftPos %>% ggplot(aes(x = Pick, y = wAV)) +
-  geom_jitter(aes(draftT$Pick, draftT$wAV), colour = "red") + 
-  stat_smooth(aes(draftT$Pick, draftT$wAV, col = "red"),
-              method = lm,
-              formula = y~log(x),
-              se = TRUE,
-              ) +
-  geom_jitter(aes(draftQB$Pick, draftQB$wAV), colour = "blue") + 
-  stat_smooth(aes(draftQB$Pick, draftQB$wAV, col = "blue"),
-              method = lm,
+attach(draftDT) 
+reg1 = lm(draftDT$wAV~draftDT$Pick)
+reg2 = lm(draftDT$wAV~log(draftDT$Pick))
+jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))
+
+p = draftDT %>% ggplot(aes(x = Pick, y = wAV)) +
+  geom_point() + 
+  stat_smooth(method = lm,
               formula = y~log(x),
@@
               )
+p
+p2 = ggplot_build(p)
+p2$data[[2]]
+
+draftDTOrder = draftDT %>%
+  group_by(Draft) %>%
+  mutate(NumPosInDraft = n()) %>%
+  mutate(PosDraft = 1:NumPosInDraft) %>%
+  arrange(PosDraft) %>%
+  ungroup(Draft)
+
+attach(draftDTOrder) 
+reg1 = lm(draftDTOrder$wAV~draftDTOrder$PosDraft)
+reg2 = lm(draftDTOrder$wAV~log(draftDTOrder$PosDraft))
+jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))
+
+p3 = draftDTOrder %>%
+  ggplot(aes(x=PosDraft, y=wAV)) +
+  geom_point() +
+  stat_smooth(method = lm,
+              formula = y~log(x),
+              se = TRUE,
+              )
+p3
+p4 = ggplot_build(p3)
+p4$data[[2]]
 ```
+Position: C
+```{r}
+draftC = draft %>%
+  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
+  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
+  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
+  filter(Pos == "C") %>%
+  filter(Draft < 2011) %>%
+  arrange(Pick)
+
+attach(draftC) 
+reg1 = lm(draftC$wAV~draftC$Pick)
+reg2 = lm(draftC$wAV~log(draftC$Pick))
+jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))
+
+p = draftC %>% ggplot(aes(x = Pick, y = wAV)) +
+  geom_point() + 
+  stat_smooth(method = lm,
+              formula = y~log(x),
+              se = TRUE,
+              )
+p
+p2 = ggplot_build(p)
+p2$data[[2]]
+
+draftCOrder = draftC %>%
+  group_by(Draft) %>%
+  mutate(NumPosInDraft = n()) %>%
+  mutate(PosDraft = 1:NumPosInDraft) %>%
+  arrange(PosDraft) %>%
+  ungroup(Draft)
+
+attach(draftCOrder) 
+reg1 = lm(draftCOrder$wAV~draftCOrder$PosDraft)
+reg2 = lm(draftCOrder$wAV~log(draftCOrder$PosDraft))
+jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))
+
+p3 = draftCOrder %>%
+  ggplot(aes(x=PosDraft, y=wAV)) +
+  geom_point() +
+  stat_smooth(method = lm,
+              formula = y~log(x),
+              se = TRUE,
+              )
+p3
+p4 = ggplot_build(p3)
+p4$data[[2]]
+```
+Position: G
+```{r}
+draftG = draft %>%
+  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
+  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
+  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
+  filter(Pos == "G") %>%
+  filter(Draft < 2011) %>%
+  arrange(Pick)
+
+attach(draftG) 
+reg1 = lm(draftG$wAV~draftG$Pick)
+reg2 = lm(draftG$wAV~log(draftG$Pick))
+jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))
+
+p = draftG %>% ggplot(aes(x = Pick, y = wAV)) +
+  geom_point() + 
+  stat_smooth(method = lm,
+              formula = y~log(x),
+              se = TRUE,
+              )
+p
+p2 = ggplot_build(p)
+p2$data[[2]]
+
+draftGOrder = draftG %>%
+  group_by(Draft) %>%
+  mutate(NumPosInDraft = n()) %>%
+  mutate(PosDraft = 1:NumPosInDraft) %>%
+  arrange(PosDraft) %>%
+  ungroup(Draft)
+
+attach(draftGOrder) 
+reg1 = lm(draftGOrder$wAV~draftGOrder$PosDraft)
+reg2 = lm(draftGOrder$wAV~log(draftGOrder$PosDraft))
+jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))
+
+p3 = draftGOrder %>%
+  ggplot(aes(x=PosDraft, y=wAV)) +
+  geom_point() +
+  stat_smooth(method = lm,
+              formula = y~log(x),
+              se = TRUE,
+              )
+p3
+p4 = ggplot_build(p3)
+p4$data[[2]]
+```
+Position: LB
+```{r}
+draftLB = draft %>%
+  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
+  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
+  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
+  filter(Pos == "LB") %>%
+  filter(Draft < 2011) %>%
+  arrange(Pick)
+
+attach(draftLB) 
+reg1 = lm(draftLB$wAV~draftLB$Pick)
+reg2 = lm(draftLB$wAV~log(draftLB$Pick))
+jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))
+
+p = draftLB %>% ggplot(aes(x = Pick, y = wAV)) +
+  geom_point() + 
+  stat_smooth(method = lm,
+              formula = y~log(x),
+              se = TRUE,
+              )
+p
+p2 = ggplot_build(p)
+p2$data[[2]]
+
+draftLBOrder = draftLB %>%
+  group_by(Draft) %>%
+  mutate(NumPosInDraft = n()) %>%
+  mutate(PosDraft = 1:NumPosInDraft) %>%
+  arrange(PosDraft) %>%
+  ungroup(Draft)
+
+attach(draftLBOrder) 
+reg1 = lm(draftLBOrder$wAV~draftLBOrder$PosDraft)
+reg2 = lm(draftLBOrder$wAV~log(draftLBOrder$PosDraft))
+jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))
+
+p3 = draftLBOrder %>%
+  ggplot(aes(x=PosDraft, y=wAV)) +
+  geom_point() +
+  stat_smooth(method = lm,
+              formula = y~log(x),
+              se = TRUE,
+              )
+p3
+p4 = ggplot_build(p3)
+p4$data[[2]]
+```
+Position: RB
+```{r}
+draftRB = draft %>%
+  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
+  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
+  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
+  filter(Pos == "RB") %>%
+  filter(Draft < 2011) %>%
+  arrange(Pick)
+
+attach(draftRB) 
+reg1 = lm(draftRB$wAV~draftRB$Pick)
+reg2 = lm(draftRB$wAV~log(draftRB$Pick))
+jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))
+
+p = draftRB %>% ggplot(aes(x = Pick, y = wAV)) +
+  geom_point() + 
+  stat_smooth(method = lm,
+              formula = y~log(x),
+              se = TRUE,
+              )
+p
+p2 = ggplot_build(p)
+p2$data[[2]]
+
+draftRBOrder = draftRB %>%
+  group_by(Draft) %>%
+  mutate(NumPosInDraft = n()) %>%
+  mutate(PosDraft = 1:NumPosInDraft) %>%
+  arrange(PosDraft) %>%
+  ungroup(Draft)
+
+attach(draftRBOrder) 
+reg1 = lm(draftRBOrder$wAV~draftRBOrder$PosDraft)
+reg2 = lm(draftRBOrder$wAV~log(draftRBOrder$PosDraft))
+jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))
+
+p3 = draftRBOrder %>%
+  ggplot(aes(x=PosDraft, y=wAV)) +
+  geom_point() +
+  stat_smooth(method = lm,
+              formula = y~log(x),
+              se = TRUE,
+              )
+p3
+p4 = ggplot_build(p3)
+p4$data[[2]]
+```
+Position: DB
+```{r}
+draftDB = draft %>%
+  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
+  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
+  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
+  filter(Pos == "DB") %>%
+  filter(Draft < 2011) %>%
+  arrange(Pick)
+
+attach(draftDB) 
+reg1 = lm(draftDB$wAV~draftDB$Pick)
+reg2 = lm(draftDB$wAV~log(draftDB$Pick))
+jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))
+
+p = draftDB %>% ggplot(aes(x = Pick, y = wAV)) +
+  geom_point() + 
+  stat_smooth(method = lm,
+              formula = y~log(x),
+              se = TRUE,
+              )
+p
+p2 = ggplot_build(p)
+p2$data[[2]]
+
+draftDBOrder = draftDB %>%
+  group_by(Draft) %>%
+  mutate(NumPosInDraft = n()) %>%
+  mutate(PosDraft = 1:NumPosInDraft) %>%
+  arrange(PosDraft) %>%
+  ungroup(Draft)
+
+attach(draftDBOrder) 
+reg1 = lm(draftDBOrder$wAV~draftDBOrder$PosDraft)
+reg2 = lm(draftDBOrder$wAV~log(draftDBOrder$PosDraft))
+jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))
+
+p3 = draftDBOrder %>%
+  ggplot(aes(x=PosDraft, y=wAV)) +
+  geom_point() +
+  stat_smooth(method = lm,
+              formula = y~log(x),
+              se = TRUE,
+              )
+p3
+p4 = ggplot_build(p3)
+p4$data[[2]]
+```
+Position: WR
+```{r}
+draftWR = draft %>%
+  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
+  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
+  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
+  filter(Pos == "WR") %>%
+  filter(Draft < 2011) %>%
+  arrange(Pick)
+
+attach(draftWR) 
+reg1 = lm(draftWR$wAV~draftWR$Pick)
+reg2 = lm(draftWR$wAV~log(draftWR$Pick))
+jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))
+
+p = draftWR %>% ggplot(aes(x = Pick, y = wAV)) +
+  geom_point() + 
+  stat_smooth(method = lm,
+              formula = y~log(x),
+              se = TRUE,
+              )
+p
+p2 = ggplot_build(p)
+p2$data[[2]]
+
+draftWROrder = draftWR %>%
+  group_by(Draft) %>%
+  mutate(NumPosInDraft = n()) %>%
+  mutate(PosDraft = 1:NumPosInDraft) %>%
+  arrange(PosDraft) %>%
+  ungroup(Draft)
+
+attach(draftWROrder) 
+reg1 = lm(draftWROrder$wAV~draftWROrder$PosDraft)
+reg2 = lm(draftWROrder$wAV~log(draftWROrder$PosDraft))
+jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))
+
+p3 = draftWROrder %>%
+  ggplot(aes(x=PosDraft, y=wAV)) +
+  geom_point() +
+  stat_smooth(method = lm,
+              formula = y~log(x),
+              se = TRUE,
+              )
+p3
+p4 = ggplot_build(p3)
+p4$data[[2]]
+```
+Position: TE
+```{r}
+draftTE = draft %>%
+  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
+  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
+  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
+  filter(Pos == "TE") %>%
+  filter(Draft < 2011) %>%
+  arrange(Pick)
+
+attach(draftTE) 
+reg1 = lm(draftTE$wAV~draftTE$Pick)
+reg2 = lm(draftTE$wAV~log(draftTE$Pick))
+jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))
+
+p = draftTE %>% ggplot(aes(x = Pick, y = wAV)) +
+  geom_point() + 
+  stat_smooth(method = lm,
+              formula = y~log(x),
+              se = TRUE,
+              )
+p
+p2 = ggplot_build(p)
+p2$data[[2]]
+
+draftTEOrder = draftTE %>%
+  group_by(Draft) %>%
+  mutate(NumPosInDraft = n()) %>%
+  mutate(PosDraft = 1:NumPosInDraft) %>%
+  arrange(PosDraft) %>%
+  ungroup(Draft)
+
+attach(draftTEOrder) 
+reg1 = lm(draftTEOrder$wAV~draftTEOrder$PosDraft)
+reg2 = lm(draftTEOrder$wAV~log(draftTEOrder$PosDraft))
+jtools::export_summs(reg1, reg2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))
+
+p3 = draftTEOrder %>%
+  ggplot(aes(x=PosDraft, y=wAV)) +
+  geom_point() +
+  stat_smooth(method = lm,
+              formula = y~log(x),
+              se = TRUE,
+              )
+p3
+p4 = ggplot_build(p3)
+p4$data[[2]]
+```
+
 ```{r}
 draft %>%
-  filter(Player == "Joe Webb")
+  mutate(Pos = replace(Pos, Pos == "SAF", "DB")) %>%
+  mutate(Pos = replace(Pos, Pos == "NT", "DT")) %>%
+  mutate(Pos = replace(Pos, Pos == "OT", "T")) %>%
+  filter(Draft < 2011) %>%
+  group_by(Pos) %>%
+  summarize(avgwAV = mean(wAV)) %>%
+  arrange(desc(avgwAV))
+
+draft %>%
+  filter(Draft < 2011) %>%
+  group_by(Pos) %>%
+  summarize(avgwAV = mean(wAV))
+draft %>%
+  filter(Pos == "DL")
 ```

### 2023-05-07 DraftPlayerPrediction.Rmd
Add files via upload

---
title: "Untitled"
output: word_document
date: "2023-04-21"
---

#load cleaned data
```{r}
library(tidyverse)
library(readxl)
library(dplyr)

draft = read_excel('1993-2022draftStats.xlsx', col_names = TRUE)
draft

draft$wAV[is.na(draft$wAV)] = 0
draft$DrAV[is.na(draft$DrAV)] = 0
draft$G[is.na(draft$G)] = 0
draft$Cmp[is.na(draft$Cmp)] = 0
draft$PassAtt[is.na(draft$PassAtt)] = 0
draft$PassYds[is.na(draft$PassYds)] = 0
draft$PassTD[is.na(draft$PassTD)] = 0
draft$`Int(O)`[is.na(draft$`Int(O)`)] = 0
draft$RushAtt[is.na(draft$RushAtt)] = 0
draft$RushYds[is.na(draft$RushYds)] = 0
draft$RushTD[is.na(draft$RushTD)] = 0
draft$Rec[is.na(draft$Rec)] = 0
draft$RecYds[is.na(draft$RecYds)] = 0
draft$RecTD[is.na(draft$RecTD)] = 0
draft$Solo[is.na(draft$Solo)] = 0
draft$`Int(D)`[is.na(draft$`Int(D)`)] = 0
draft$Sk[is.na(draft$Sk)] = 0
draft$`College/Univ`[3051] = "Bethel (TN)"
draft$`College/Univ`[3145] = "Lousiana-Lafayette"
draft$`College/Univ`[3149] = "Regina"
draft$`College/Univ`[3170] = "Lousiana-Lafayette"
draft$`College/Univ`[3229] = "California Polytechnic State"
draft$`College/Univ`[3231] = "Missouri Western State"
draft$`College/Univ`[3249] = "Georgia State"
draft$`College/Univ`[3261] = "Alabama-Birmingham"
draft$`College/Univ`[3516] = "Colorado State-Pueblo"
draft$`College/Univ`[3555] = "Northeastern State"
draft$`College/Univ`[4259] = "No college"
draft$`College/Univ`[4818] = "No college"
draft$`College/Univ`[6046] = "Eastern Michigan"
draft$`College/Univ`[6843] = "Trinity International"
draft$`College/Univ`[7097] = "Trinity International"
draft$`College/Univ`[7296] = "Clark Atlanta"

combine = read_excel('1993-2022combineData.xlsx', col_names = TRUE)
combine

colnames(combine)[1] <- "Draft"
colnames(combine)[2] <- "Player"
colnames(combine)[4] <- "Pos"
combine = combine %>%
  drop_na(Player)
combine

combinePast = combine %>%
  filter(Draft < 2023)

combinePast = combinePast[,-3]
combinePast = combinePast[,-3]

draftCombine = merge(x = draft, y = combinePast, by = c("Player", "Draft"), all.x = TRUE)
draftCombine
```
```{r}
bigChartQB %>%
  group_by(Conf) %>%
  summarise(meanwAV = mean(wAV)) %>%
  arrange(desc(meanwAV))

bigChartQB %>%
  group_by(level) %>%
  summarise(meanwAV = mean(wAV)) %>%
  arrange(desc(meanwAV))
```

```{r}
bigChartQB %>% ggplot(aes(x = `Weight (lbs)`, y = wAV)) +
  geom_point() + 
  stat_smooth(method = lm,
              formula = y~x^2,
              se = TRUE,
              )

bigChartQB %>%
  filter(complete.cases(`Height (in)`)) %>%
  ggplot(aes(x = `Height (in)`, y = wAV)) +
  geom_point()

bigChartQB %>%
  filter(complete.cases(`Weight (lbs)`)) %>%
  ggplot(aes(x = `Weight (lbs)`, y = wAV)) +
  geom_point()

bigChartQB %>%
  filter(complete.cases(`Hand Size (in)`)) %>%
  ggplot(aes(x = `Hand Size (in)`, y = wAV)) +
  geom_point()

bigChartQB %>%
  filter(complete.cases(`Arm Length (in)`)) %>%
  ggplot(aes(x = `Arm Length (in)`, y = wAV)) +
  geom_point()

bigChartQB %>%
  filter(complete.cases(Wonderlic)) %>%
  ggplot(aes(x = Wonderlic, y = wAV)) +
  geom_point()

bigChartQB %>%
  filter(complete.cases(`40 Yard`)) %>%
  ggplot(aes(x = `40 Yard`, y = wAV)) +
  geom_point()

bigChartQB %>%
  filter(complete.cases(`Vert Leap (in)`)) %>%
  ggplot(aes(x = `Vert Leap (in)`, y = wAV)) +
  geom_point()

```
```{r}
mod1 = lm(bigChartQB$wAV~I(bigChartQB$`Arm Length (in)`^2))
mod2 = lm(bigChartQB$wAV~bigChartQB$CollegeRAvg)
jtools::export_summs(mod1, mod2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))
```

```{r}
#all sig left
regQB1 = lm(bigChartQB$wAV~bigChartQB$`Hand Size (in)` + bigChartQB$CollegeRYds + bigChartQB$CollegeRAvg)
#all
regQB2 = lm(bigChartQB$wAV ~ bigChartQB$`Height (in)` + bigChartQB$`Hand Size (in)` + bigChartQB$`Weight (lbs)` + bigChartQB$`Arm Length (in)`
            + bigChartQB$`40 Yard` + bigChartQB$`Vert Leap (in)` + bigChartQB$`Broad Jump (in)` + bigChartQB$Shuttle + bigChartQB$`3Cone`
            + bigChartQB$CollegeG + bigChartQB$CollegeAtt + bigChartQB$CollegeCmp + bigChartQB$CollegePct 
            + bigChartQB$CollegeRYds + bigChartQB$CollegeYds + bigChartQB$`CollegeAY/A` + bigChartQB$`CollegeY/A` + bigChartQB$CollegeTD
            + bigChartQB$CollegeInt + bigChartQB$CollegeRTD + bigChartQB$CollegeRate + bigChartQB$CollegeRAtt + bigChartQB$CollegeRAvg)
#one by one
regQB3 = lm(bigChartQB$wAV~bigChartQB$CollegeRYds)
#one by one sig all
regQB4 = lm(bigChartQB$wAV~bigChartQB$`Height (in)` + bigChartQB$`Weight (lbs)` + bigChartQB$`Hand Size (in)` + bigChartQB$`Vert Leap (in)` 
            + bigChartQB$CollegePct)
#one by one sig all left
regQB5 = lm(bigChartQB$wAV~bigChartQB$`Hand Size (in)`)
#one by one sig all each left
regQB6 = lm(bigChartQB$wAV~bigChartQB$`Height (in)` + bigChartQB$CollegePct)
#sig values: Height3, Weight2, HandSize2, Wonderlic2, Vertical Leap1, CollegePct1
#not sig values: armlength, 40yard, BroadJump, Shuttle, 3Cone, CollegeG, CollegeCmp, CollegeAtt, CollegeYds, CollegeTD, CollegeAYA, CollegeYA, Int, Rate, Rush
jtools::export_summs(regQB1, regQB2, regQB3, regQB4, regQB5, regQB6, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))
```
```{r}
Power5QB = bigChartQB %>%
  filter(level == "Power")

modP1 = lm(Power5QB$wAV~I(Power5QB$CollegeRAvg^2))
modP2 = lm(Power5QB$wAV~Power5QB$CollegeRAvg)
jtools::export_summs(modP1, modP2, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))

#sig values: Height2, CollegePct1, 
regPQB = lm(Power5QB$wAV~I(Power5QB$`Height (in)`^2) + Power5QB$CollegePct)
regPQBallquad = lm(Power5QB$wAV~I(Power5QB$`Height (in)`^2) + Power5QB$`Hand Size (in)` + Power5QB$`Weight (lbs)` + Power5QB$`Arm Length (in)`
                   + I(Power5QB$`40 Yard`^2) + Power5QB$`Vert Leap (in)` + Power5QB$`Broad Jump (in)` + Power5QB$Shuttle + Power5QB$`3Cone`
                   + Power5QB$CollegeG + I(Power5QB$CollegeAtt^2) + I(Power5QB$CollegeCmp^2) + Power5QB$CollegePct + I(Power5QB$CollegeRYds^2) 
                   + I(Power5QB$CollegeYds^2) + Power5QB$`CollegeAY/A` + Power5QB$`CollegeY/A` + Power5QB$CollegeTD + Power5QB$CollegeInt
                   + Power5QB$CollegeRTD + Power5QB$CollegeRate + Power5QB$CollegeRAtt + Power5QB$CollegeRAvg)
regPQBall = lm(Power5QB$wAV ~ Power5QB$`Height (in)` + Power5QB$`Hand Size (in)` + Power5QB$`Weight (lbs)` + Power5QB$`Arm Length (in)`
            + Power5QB$`40 Yard` + Power5QB$`Vert Leap (in)` + Power5QB$`Broad Jump (in)` + Power5QB$Shuttle + Power5QB$`3Cone`
            + Power5QB$CollegeG + Power5QB$CollegeAtt + Power5QB$CollegeCmp + Power5QB$CollegePct 
            + Power5QB$CollegeRYds + Power5QB$CollegeYds + Power5QB$`CollegeAY/A` + Power5QB$`CollegeY/A` + Power5QB$CollegeTD
            + Power5QB$CollegeInt + Power5QB$CollegeRTD + Power5QB$CollegeRate + Power5QB$CollegeRAtt + Power5QB$CollegeRAvg)
regPQBallsig = lm(Power5QB$wAV ~ Power5QB$`Height (in)` + Power5QB$`Hand Size (in)`+ Power5QB$`40 Yard` 
            + Power5QB$CollegeYds + Power5QB$CollegeRAvg)
jtools::export_summs(regPQB, regPQBallquad, regPQBall, regPQBallsig, digits=3, statistics = c(N = "nobs",R2 = "r.squared",AIC = "AIC",BIC = "BIC"))
```

### 2023-05-07 NFLdraftDataCleaning.R

@@ -1,0 +1,177 @@
+#NFL draft data cleaning
+library(tidyverse)
+library(readxl)
+
+draft = read_excel('1993-2022draftStats.xlsx', col_names = TRUE)
+draft
+
+#Cleaning of data
+#-Fixing NA values
+colnames(draft)
+which(is.na(draft$Draft))#none
+which(is.na(draft$Rnd))#none
+which(is.na(draft$Pick))#none
+which(is.na(draft$Tm))#none
+which(is.na(draft$Player))#none
+which(is.na(draft$Pos))#none
+which(is.na(draft$Age))#not as important so we can leave as NA
+draft %>%
+  filter(is.na(draft$Age))
+
+which(is.na(draft$To))#not as important so we can leave as NA
+draft %>%
+  filter(is.na(draft$To))
+
+which(is.na(draft$AP1))#none
+which(is.na(draft$PB))#none
+which(is.na(draft$St))#none
+which(is.na(draft$wAV))#important need to change
+draft %>%
+  filter(is.na(draft$wAV))
+#After looking at the data it seems like a majority of the reason wAV is NA is
+#because the player did not play any games or they got cut etc. So I am going
+#to set every NA value to 0
+draft$wAV[is.na(draft$wAV)] = 0
+which(is.na(draft$wAV))#data is fixed to none
+
+which(is.na(draft$DrAV))#important need to change
+draft %>%
+  filter(is.na(draft$DrAV))
+#After looking at the data it seems that like a majority of the reason DrAV is NA
+#is because the player did not play any games or they got cut or they were traded
+#before playing for the drafted team. So I am going to change all values to 0
+draft$DrAV[is.na(draft$DrAV)] = 0
+which(is.na(draft$DrAV))#data is fixed to none
+
+which(is.na(draft$G))#needs change
+draft %>%
+  filter(is.na(draft$G))
+#A majority of the people that have NA for games never played in any, so I
+#am changing all NA's to 0
+draft$G[is.na(draft$G)] = 0
+which(is.na(draft$G))#data is fixed to none
+
+which(is.na(draft$Cmp))#same thing as above
+draft$Cmp[is.na(draft$Cmp)] = 0
+which(is.na(draft$Cmp))
+
[…]

### 2023-05-07 combineDataCleaning.R

@@ -1,0 +1,471 @@
+#College Player Analysis
+library(tidyverse)
+library(readxl)
+library(dplyr)
+
+draft = read_excel('1993-2022draftStats.xlsx', col_names = TRUE)
+draft
+
+draft$wAV[is.na(draft$wAV)] = 0
+draft$DrAV[is.na(draft$DrAV)] = 0
+draft$G[is.na(draft$G)] = 0
+draft$Cmp[is.na(draft$Cmp)] = 0
+draft$PassAtt[is.na(draft$PassAtt)] = 0
+draft$PassYds[is.na(draft$PassYds)] = 0
+draft$PassTD[is.na(draft$PassTD)] = 0
+draft$`Int(O)`[is.na(draft$`Int(O)`)] = 0
+draft$RushAtt[is.na(draft$RushAtt)] = 0
+draft$RushYds[is.na(draft$RushYds)] = 0
+draft$RushTD[is.na(draft$RushTD)] = 0
+draft$Rec[is.na(draft$Rec)] = 0
+draft$RecYds[is.na(draft$RecYds)] = 0
+draft$RecTD[is.na(draft$RecTD)] = 0
+draft$Solo[is.na(draft$Solo)] = 0
+draft$`Int(D)`[is.na(draft$`Int(D)`)] = 0
+draft$Sk[is.na(draft$Sk)] = 0
+draft$`College/Univ`[3051] = "Bethel (TN)"
+draft$`College/Univ`[3145] = "Lousiana-Lafayette"
+draft$`College/Univ`[3149] = "Regina"
+draft$`College/Univ`[3170] = "Lousiana-Lafayette"
+draft$`College/Univ`[3229] = "California Polytechnic State"
+draft$`College/Univ`[3231] = "Missouri Western State"
+draft$`College/Univ`[3249] = "Georgia State"
+draft$`College/Univ`[3261] = "Alabama-Birmingham"
+draft$`College/Univ`[3516] = "Colorado State-Pueblo"
+draft$`College/Univ`[3555] = "Northeastern State"
+draft$`College/Univ`[4259] = "No college"
+draft$`College/Univ`[4818] = "No college"
+draft$`College/Univ`[6046] = "Eastern Michigan"
+draft$`College/Univ`[6843] = "Trinity International"
[…]

### 2023-05-07 tradeAnalyzer.java
Add files via upload

@@ -1,0 +1,401 @@
+//package SeniorCapstoneProjectApplication;
+
+import java.util.Scanner;
+
+public class tradeAnalyzer {
+
+	public static void main(String[] args) {
+		
+		Scanner input = new Scanner(System.in);
+		
+		Double[] regressionValues = new Double[270];
+		
+		regressionValues[1] = 79.710258829259;
+		regressionValues[2] = 70.2706486154282;
+		regressionValues[3] = 64.7488306189113;
+		regressionValues[4] = 60.8310384015976;
+		regressionValues[5] = 57.7921626689812;
+		regressionValues[6] = 55.3092204050847;
+		regressionValues[7] = 53.2099226331595;
+		regressionValues[8] = 51.391428187771;
+		regressionValues[9] = 49.7874024085717;
+		regressionValues[10] = 48.3525524551546;
+		regressionValues[11] = 47.0545727879275;
+		regressionValues[12] = 45.8696101912581;
+		regressionValues[13] = 44.7795502702366;
+		regressionValues[14] = 43.7703124193329;
+		regressionValues[15] = 42.8307344586416;
+		regressionValues[16] = 41.9518179739444;
+		regressionValues[17] = 41.1262028443474;
+		regressionValues[18] = 40.3477921947451;
+		regressionValues[19] = 39.6114788857537;
+		regressionValues[20] = 38.912942241328;
+		regressionValues[21] = 38.2484944228199;
+		regressionValues[22] = 37.6149625741009;
+		regressionValues[23] = 37.0095971859776;
+		regressionValues[24] = 36.4299999774315;
+		regressionValues[25] = 35.8740665087115;
+		regressionValues[26] = 35.33994005641;
+		regressionValues[27] = 34.8259741982321;
+		regressionValues[28] = 34.3307022055063;
+		regressionValues[29] = 33.8528118090691;
+		regressionValues[30] = 33.391124244815;
+		regressionValues[31] = 32.9445767364208;
+		regressionValues[32] = 32.5122077601178;
+		regressionValues[33] = 32.0931445775879;
+		regressionValues[34] = 31.6865926305208;
+		regressionValues[35] = 31.2918264728898;
+		regressionValues[36] = 30.9081819809185;
+		regressionValues[37] = 30.5350496306065;
+		regressionValues[38] = 30.1718686719271;
+		regressionValues[39] = 29.818122059897;
+		regressionValues[40] = 29.4733320275014;
[…]
